Adding Sensitivity to 21cm Inteferometric Probes of Reionization by Optimizing Choice of Baselines

### 2017-03-30 Rotation paper/draft_working.tex
save

Having defined the modified weight $\widetilde{\Theta}$, we can estimate the power spectrum by inverse covariance weighting:
\begin{equation}
\begin{aligned}
 P(k_{\tau}) &= \frac{\sum_{bb'}P(k_{b,\tau})/\sigma_P^2(bb')}{\sum_{bb'}\sigma_P^2(bb')}, \\
 &= \frac{\sum_{bb'}P(k_{b,\tau})\widetilde{\Theta}_{bb'}^2}{\sum_{bb'}\widetilde{\Theta}_{bb'}^2},
 \end{aligned}
\end{equation}
where the sum is over classes of baseline pairs. 
We define the estimator sensitivity to be the inverse of the power-spectrum noise variance:
\begin{equation}
\rho \propto \frac{1}{\sigma_P^2} \propto \frac{1}{\sigma^4_N}\sum_{bb'}^N\widetilde{\Theta}^2_{bb'},
\end{equation}
where $\sigma_N$ is a characteristic single-baseline noise level.

The scaling in Eq. \ref{eq:sensul} was rough for simplicity of motivation. As we derive in Appendix \ref{sec:appB}, this weight should be corrected by a factor proportional to the signal to noise ratio of a single-baseline visibility $\rho_0=\sigma_S^2/\sigma_N^2$:

>>>>

Having defined the modified weight $\widetilde{\Theta}$, we can estimate the power spectrum by inverse covariance weighting:
\begin{equation}
\begin{aligned}
 P(k_{\tau}) &= \frac{\sum_{bb'}P(k_{b,\tau})/\sigma_P^2(bb')}{\sum_{bb'}\sigma_P^2(bb')}, \\
 &= \frac{\sum_{bb'}P(k_{b,\tau})\widetilde{\Theta}_{bb'}^2}{\sum_{bb'}\widetilde{\Theta}_{bb'}^2},
 \end{aligned}
\end{equation}
where the sum is over classes of baseline pairs. 
We define the estimator sensitivity to be the inverse of the power-spectrum noise variance:
\begin{equation}
\rho \propto \frac{1}{\sigma_P^2} \propto \rho_0^2\sum_{bb'}^N\widetilde{\Theta}^2_{bb'},
\end{equation}
where, if $\sigma_S^2$ and $\sigma_N^2$ are the characteristic signal and noise levels of a single-baseline visibility, $\rho_0=\sigma_S^2/\sigma_N^2$ is the signal to noise ratio.

The scaling in Eq. \ref{eq:sensul} was rough for simplicity of motivation. As we derive in Appendix \ref{sec:appB}, this weight should be corrected by a factor proportional $\rho_0$:
